Proposed Solution

### 2016-01-29 intro1.tex
config: intro

\begin{figure}[t] \centering
\includegraphics[width=0.65\textwidth]{figs/overview}
\caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
  including both correct general configuration files and users' input
  configuration files. The purple boxes are the components within \app.
  The yellow boxes are results generated by \app's components.}}
\label{fig-overview}
\end{figure}

@@

  \item We designed and implemented a tool, \app, that can learn a language model from an example set of correct configuration files, and we use the model to verify new files.
  \item We use probabilistic types to assign a confidence distribution over a set of types to a value.
  \item In \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

>>>>

\begin{figure}[t] \centering
\includegraphics[width=0.63\textwidth]{figs/overview}
\caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
  including both correct general configuration files and users' input
  configuration files. The purple boxes are the components within \app.
  The yellow boxes are results generated by \app's components.}}
\label{fig-overview}
\end{figure}

@@

  \item We designed and implemented a tool, \app, that can learn a
language model from an example set of correct configuration files, and
we use the model to verify new configuration files.
  \item We use probabilistic types to assign a confidence distribution over a set of types to a value.
  \item In \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
